\chapter{Host Organisation and Industry Context}
\section{Company Overview}
The client is a confidential European ecommerce platform provider with a gross merchandise volume of EUR 1.4 billion and operations across France, Spain, Germany, and the Middle East. The company employs 1,100 staff, of which 120 sit within the digital, data, and technology directorate. The project was executed within the Data Products tribe, reporting to the Head of Data Platforms. Key characteristics include:
\begin{itemize}
    \item \textbf{Multi-brand portfolio:} Fashion, lifestyle, and home-improvement brands sharing fulfilment centres and marketing teams.
    \item \textbf{Hybrid infrastructure:} Core transactional systems hosted on Azure, with analytics workloads split between \gls{aws} and on-premises PostgreSQL clusters.
    \item \textbf{Marketplace expansion:} Third-party sellers account for 35\% of revenue, generating heterogenous data formats and SLA commitments.
    \item \textbf{Data governance mandate:} A corporate initiative to align with ISO/IEC 27001 and GDPR accountability requirements.
\end{itemize}

\section{Stakeholder Map}
The programme engaged a cross-functional stakeholder group summarised in Table~\ref{tab:stakeholders}. Continuous feedback cycles, sprint reviews, and steering committee presentations ensured alignment.

\begin{table}[H]
    \centering
    \caption{Stakeholder responsibilities and success indicators}
    \label{tab:stakeholders}
    \begin{tabularx}{\textwidth}{|l|X|X|}
        \hline
        \textbf{Role} & \textbf{Responsibilities} & \textbf{Success Indicators} \\
        \hline
        Chief Digital Officer & Portfolio prioritisation, investment approval, governance oversight & Launch of unified KPI platform, compliance audit pass \\
        \hline
        Director of Data Products & Product roadmap, backlog curation, KPI definition & Adoption across merchandising, marketing, support teams \\
        \hline
        Head of Customer Care & Voice-of-customer integration, escalation procedures & 15\% reduction in average handling time, CSAT improvement \\
        \hline
        Lead DevOps Engineer & Infrastructure automation, observability, incident response & Zero unplanned downtime during go-live, automated recovery \\
        \hline
        Finance Business Partner & Benefit realisation tracking, cost management & Quarterly reporting automation, cost-to-serve transparency \\
        \hline
    \end{tabularx}
\end{table}

\section{Competitive Benchmark}
Industry benchmarking identified leading ecommerce organisations deploying similar capabilities. Insights from Shopify, Zalando, and Amazon Retail emphasised:
\begin{itemize}
    \item Near real-time dashboards with predictive overlays to manage supply chain risk.
    \item Unified data contracts enabling consistent KPIs across digital and physical channels.
    \item Federated data product governance to accelerate onboarding of new domains.
\end{itemize}

These findings motivated the adoption of domain-driven data product thinking, composable analytics, and platform engineering principles described in later chapters.
