\chapter{Operations, Automation, and Governance}
\section{Continuous Integration and Delivery}
The automation stack integrates Jenkins pipelines, GitHub Actions, and Terraform Cloud. Figure~\ref{fig:cicd-flow} illustrates the deployment flow.

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node distance=2.2cm,>=stealth',thick]
        \tikzstyle{stage}=[rectangle, rounded corners=2mm, draw=green!60!black, fill=green!10, minimum width=3.2cm, minimum height=1cm]
        \tikzstyle{arrow}=[->, line width=0.8pt, color=green!60!black]
        \node[stage] (commit) {Code Commit};
        \node[stage, right=2.8cm of commit] (ci) {Static Analysis\\Unit Tests};
        \node[stage, right=2.8cm of ci] (package) {Container Build\\Artifact Publish};
        \node[stage, right=2.8cm of package] (plan) {Terraform Plan\\Peer Review};
        \node[stage, right=2.8cm of plan] (deploy) {Blue/Green Deploy\\Automated Tests};
        \draw[arrow] (commit) -- (ci);
        \draw[arrow] (ci) -- (package);
        \draw[arrow] (package) -- (plan);
        \draw[arrow] (plan) -- (deploy);
    \end{tikzpicture}
    \caption{CI/CD orchestration flow}
    \label{fig:cicd-flow}
\end{figure}

Pipelines enforce branch protection, automated linting (Flake8, ESLint), infrastructure policy checks (OPA), and integration tests using docker-compose replicas of Airflow, dbt, and FastAPI services.

\section{Security and Compliance}
\begin{itemize}
    \item \textbf{Identity:} AWS IAM and Azure Active Directory enforce least privilege via role-based access control and Just-In-Time elevation.
    \item \textbf{Secrets:} AWS Secrets Manager and Azure Key Vault integrate with Terraform and Jenkins, ensuring rotation and auditability.
    \item \textbf{Network:} Private subnets, Transit Gateway connectivity, and Azure ExpressRoute secure data flows between clouds and on-premises systems.
    \item \textbf{Compliance:} Automated evidence collection via Cloud Custodian and Azure Policy supports ISO/IEC 27001 controls and GDPR records of processing.
\end{itemize}

\section{Observability}
Metrics, logs, and traces feed into a consolidated telemetry platform:
\begin{itemize}
    \item Prometheus-compatible metrics exported by Airflow, dbt, and FastAPI.
    \item Structured logs shipped to Amazon CloudWatch Logs and Azure Monitor, enriched with correlation IDs.
    \item Distributed tracing via OpenTelemetry integrated with Datadog APM for end-to-end request visualisation.
    \item Business KPIs surfaced in Grafana dashboards, offering single-pane-of-glass visibility for Site Reliability Engineers.
\end{itemize}

\section{Risk Management}
\begin{table}[H]
    \centering
    \caption{Risk register snapshot}
    \label{tab:risk}
    \begin{tabular}{p{3.5cm}p{3cm}p{2cm}p{6cm}}
        \toprule
        \textbf{Risk} & \textbf{Impact} & \textbf{Likelihood} & \textbf{Mitigation} \\
        \midrule
        Cloud quota exhaustion & High & Medium & Implement proactive quota monitoring, automated support tickets, and synthetic load forecasting.
\\
        Data privacy breach & Critical & Low & Enforce encryption, tokenisation, DLP scanning, and privacy impact assessments per release.
\\
        Vendor lock-in & Medium & Medium & Maintain abstraction layers, dual-provider IaC modules, and periodic portability drills.
\\
        Observability blind spots & Medium & Medium & Expand OpenTelemetry coverage, enforce logging standards, and run chaos engineering game days.
\\
        Skills gap for advanced analytics & Medium & High & Launch enablement sessions, create playbooks, and sponsor certifications.
\\
        \bottomrule
    \end{tabular}
\end{table}

\section{Cost Governance}
FinOps practices incorporate tagging, cost allocation, and budget alerts. Monthly reviews evaluate service utilisation, reserved instance coverage, and rightsizing opportunities. Non-production environments power down automatically outside business hours, delivering a 32\% reduction in monthly run rate.
